### 2017-09-30 TF-vldb2018/sec-tsimAlg.tex

\stitle{Correctness \& complexity analyses}. The correctness of \grouprec is assured by the following.
%(1) There is a unique perfect subgraph in each ball of $G$.
(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as graph simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$. However, actual time is much less due to density based ball filtering and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule
			\vspace{-3ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $r$ and $r$.\\
				{\sl Output:\/} Top-$k$ densest teams.\\
				\sstab \bcc \hspace{1ex}\= \If $P$ is unsatisfiable \Then \Return $nil$;\\
				\icc \> $L_{k} := \emptyset$;\\
				\icc \> \For each ball $\ball{[v,r]}$ in $G$ \Do\\
				\icc \>\hspace{2ex}\= compute the maximum core $\ball{}_{C}$ of the ball $\ball{[v,r]}$;\\
				\icc \>\> \If 2*$\density{\ball{}_C} <$  the density of the $k$-th result in $L_{k}$ \Then\\
				\icc  \>\>\hspace{2ex}\= \Continue;\\
				\icc \>\> $G_s$ := \rgraphsim$(P, \ball{[v,r]})$; \\
				\icc \>\> If $G_s$ satisfy capacity bounds on $P$ \Then Insert $G_s$ into $L_{k}$;\\
				\icc \>\> \For each ball $\ball{[v,t]}$ with $t\in[1,r-1]$ \Do\\
				\icc \>\>\hspace{2ex}\= $G'_s$ := \kw{incSim}$(G_s, P, \ball{[v,t]})$;\\
				\icc \>\>\> If $G'_s$ satisfy capacity bounds on $P$ \Then Insert $G'_s$ into $L_{k}$;\\
				%\icc \>\> \If $\density{G_s}>$ the density of the $k$-th result in $L_{k}$ \Then\\
				%\icc \>\> \If $\density{G_s}>$ the density of $kth$ result in $L_{k}$ and there exists\\
				%     \>\>\hspace{0.5ex}   no $G'_s$ in $L_{k}$ that is same with $G_{s}$ \Then\\
				%\icc \>\>\hspace{2ex}\= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$;\\
				\icc \>\, \Return $L_{k}[0:k-1]$.
			}

>>>>

\stitle{Correctness \& complexity analyses}. The correctness of \grouprec is assured by the following.
%(1) There is a unique perfect subgraph in each ball of $G$.

\sstab(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as graph simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).

\sstab(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$. However, actual time is much less due to density based ball filtering and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule
			\vspace{-3ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $r$ and $k$.\\
				{\sl Output:\/} Top-$k$ densest teams.\\
				\sstab \bcc \hspace{1ex}\= \If $P$ is unsatisfiable \Then \Return $nil$;\\
				\icc \> $L_{k} := \emptyset$;\\
				\icc \> \For each ball $\ball{[v,r]}$ in $G$ \Do\\
				\icc \>\hspace{2ex}\= compute the maximum core $\ball{}_{C}$ of the ball $\ball{[v,r]}$;\\
				\icc \>\> \If 2*$\density{\ball{}_C} \le$  the density of the $k$-th result in $L_{k}$ \Then\\
				\icc  \>\>\hspace{2ex}\= \Continue;\\
				\icc \>\> $G_s$ := \rgraphsim$(P, \ball{[v,r]})$; \\
				\icc \>\> If $G_s$ satisfies capacity bounds on $P$ \Then Insert $G_s$ into $L_{k}$;\\
				\icc \>\> \For each ball $\ball{[v,t]}$ with $t\in[1,r-1]$ \Do\\
				\icc \>\>\hspace{2ex}\= $G'_s$ := \kw{incSim}$(G_s, P, \ball{[v,t]})$;\\
				\icc \>\>\> If $G'_s$ satisfies capacity bounds on $P$ \Then Insert $G'_s$ into $L_{k}$;\\
				%\icc \>\> \If $\density{G_s}>$ the density of the $k$-th result in $L_{k}$ \Then\\
				%\icc \>\> \If $\density{G_s}>$ the density of $kth$ result in $L_{k}$ and there exists\\
				%     \>\>\hspace{0.5ex}   no $G'_s$ in $L_{k}$ that is same with $G_{s}$ \Then\\
				%\icc \>\>\hspace{2ex}\= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$;\\
				\icc \>\, \Return $L_{k}[0:k-1]$.
			}
